---
title: "R Notebook"
output: html_notebook
Author: "Alicia, Joram, Jago"
---
s

Aufgaben:
1. Alicia 
2. Joram
3. Jago

Whatapps

#This code chunk contains all libraries that are needed for the following code chunks. @all: Place all libraries here 
```{r libraries, message=FALSE, warning=FALSE}

```
#Setup code chunk: This code chunk contains all settings that are needed for the following code chunks. @all: Place all settings here
```{r setup}

```
#Data code chunk: This code chunk contains all code that is needed to load the data for the following code chunks. @all: Place all data loading code here
```{r data}
#loading data from storage and assigning variables for data access using a helper function to handle potential errors and warnings during the loading process
safe_read_csv <- function(path, sep = ";", header = TRUE, dec = ".") {
  tryCatch(
    {
      data <- read.csv(path, sep = sep, header = header, dec = dec)
      message("Successfully loaded: ", path)
      return(data)
    },
    warning = function(w) {
      message("Warning in file ", path, ": ", conditionMessage(w))
      return(NULL)
    },
    error = function(e) {
      message("Error in file ", path, ": ", conditionMessage(e))
      return(NULL)
    }
  )
}

#using helper function to load csv files and assign variables for data access
AS_2025 <- safe_read_csv("Daten/Ausgaben_Sommertouristen_2025_24.csv", sep = ";")
B_2025  <- safe_read_csv("Daten/Bewertungen_2025_24.csv", sep = "\n")

#variables for data access 
AS_2025 #Ausgaben_Sommertouristen_2025_24
B_2025 #Bewertungen_2025_24
```

